The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/intro.tex
Small tweaks to intro.

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, $n \in \N$\footnote{That is, integers greater than 0.}, $p \in (0,
1)$ with probability density function (pdf)

>>>>

One of the most basic distributions in probability and statistics is the
binomial, $X \sim Bin(n,p)$, $n = 1, 2, \ldots$, $p \in (0, 1)$ with
probability density function (pdf)
